CHanging to checkPEP Access

### 2018-09-20 interactiveMap.Rmd
adding push_up file for syncing to shared dropbox with IPM (goes to Mal_analyses/folder)

---
title: "PEP Access"
author: "Malavika Rajeev"
date: "6/25/2018"
output: html_document
---
```{r directory, include=FALSE}
rm(list = ls())
require("knitr")
opts_knit$set(root.dir = "/Users/mrajeev/Dropbox/MadaPEP")
```
## Data

>>>>

---
title: "CHanging to checkPEP Access"
author: "Malavika Rajeev"
date: "6/25/2018"
output: html_document
---
```{r directory, include=FALSE}
rm(list = ls())
require("knitr")
opts_knit$set(root.dir = "/Users/mrajeev/Dropbox/MadaPEP")
```
## Data
